% Use https://overleaf.com to edit this file
\documentclass[10pt]{article} % Font size 10pt/11pt/12pt

% Font
\usepackage[T1]{fontenc}
\usepackage[sfdefault,light,semibold,lf]{FiraSans}

% Margin
\usepackage{geometry}
\geometry{
    a4paper,
    margin=1.5cm
}

% Commands
\newcommand{\uthree}[4]{
    {\large
        {\bfseries #1 $|$ \textit{#2} \hfill #3} \par
    }
    \begin{itemize}
        #4
    \end{itemize}
    \par\addvspace{2.5ex}%
}

\newcommand{\ufour}[5]{
    {\large \bfseries
        #1 \hfill #2 \par
        \textit{#3 \hfill #4} \par
    }
    \begin{itemize}
        #5
    \end{itemize}
    \par\addvspace{2.5ex}%
}


% List
\usepackage{enumitem}
\setlist[itemize]{
    left=0pt .. 1.5em,
    itemsep=0.3em,
    parsep=0pt
    }

% Section
\usepackage{soul}
\usepackage[explicit]{titlesec}
\titleformat{\section}
{\large\bfseries\uppercase}
{}{}
{\hrulefill\ \so{#1} \hrulefill}

% Footer
\usepackage[page]{totalcount}
\usepackage{fancyhdr}
\usepackage{ifthen}

\AtBeginDocument{
    \ifthenelse{\totalpages>1}
    {\pagestyle{fancy}}
    {\pagestyle{empty}} % no page number if only one page
}

\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
\cfoot{\color{gray}Resume -- Page \thepage{} of \totalpages}

\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=darkgray
}

\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}

\pdfgentounicode=1

\usepackage{multicol}
\usepackage{fontawesome5}

% Resume starts here
\begin{document}

\begin{multicols}{3}
  \begin{flushleft}
    \color{gray}{\faGithub} \href{https://github.com/2kabhishek}{2KAbhishek} \\
    \color{gray}{\faEnvelope} \href{mailto:iam2kabhishek@gmail.com}{iam2kabhishek@gmail.com} \\
  \end{flushleft}

\columnbreak

  \begin{center}
      {\huge\bfseries Abhishek Keshri}
  \end{center}

\columnbreak

  \begin{flushright}
    \href{https://linkedin.com/in/2kabhishek/}{2KAbhishek} {\color{gray}{\faLinkedin}} \\
    \href{https://2kabhishek.github.io/links}{More Links} {\textcolor{gray}{\faLink}} \\
  \end{flushright}
\end{multicols}

\begin{center}
  {\bfseries Tech Lead | Full-Stack \& Developer Tooling Engineer | Open Source Maintainer}
\end{center}

\section{Summary}
%===========%
Tech Lead with 5+ years of experience building production systems and AI solutions for US healthcare clients.\\
Strong ownership across system design, architecture, globalization, dev tooling, and delivery for distributed teams.\\
Developer advocate with 4.5k+ community reach: 240+ repos, 2.2K+ GitHub stars, and active technical mentoring.

\section{Experience}
%==============%
\uthree{Tech Lead, Incubyte}{Jun 2021 -- Present}{Remote}{
  \item Led team of 11 engineers delivering systems for US healthcare clients, owning architecture, quality, and release.
  \item Led large-scale API optimization initiative, reducing infra costs by \$680K annually (40\% reduction).
  \item Led globalization and accessibility, scaling a product to 200+ countries and 57+ languages with WCAG 2.1.
  \item Built AI dev tooling and automated CI/CD workflows, reducing deployment time by 60\% (20 mins to 8 mins).
  \item Mentored engineers on clean code, AI best practices, and technical guidance, fostering collaborative culture.
}

\uthree{Project Engineer, Wipro}{Sep 2020 -- Jun 2021}{Remote}{
  \item Owned legacy system enhancements including forex support and SAP Crystal integration for LATAM client.
  \item Built custom UI framework in Java Swing, automated QA, prod deploys, reducing manual deployment overhead.
}

\uthree{Software Development Intern, Edifixio}{Dec 2018 -- Jan 2019}{Kolkata, India}{
  \item Developed Android application for real-time IoT data monitoring via Bluetooth, deployed on AWS Lambda.
  \item Optimized data processing performance and ensured system reliability.
}

\section{Open Source Impact}
%==============%
\uthree{Open Source Maintainer}{Nov 2018 -- Present}{\href{http://github.com/2kabhishek}{GitHub}}{
  \item Built and maintained 240+ open-source repos focused on dev tooling and productivity, with 2.2K+ GitHub stars.
}

\uthree{Conference Speaker}{Apr 2022 -- Present}{Various}{
  \item Spoke at NeovimConf, VimConf Tokyo and various other conferences on developer tooling and productivity.
}

\uthree{Content Creator}{Jun 2020 -- Present}{\href{http://youtube.com/@2kabhishek}{YouTube}}{
  \item Create technical content on developer tooling, productivity systems, and software development practices.
}

\uthree{Technical Mentor}{Mar 2020 -- Present}{Mentors Without Borders}{
  \item Mentor students on web development fundamentals, programming concepts, and career guidance in technology.
}

\section{Skills}
%=========%
\begin{description}
  \item[Programming Languages:] Ruby, Python, TypeScript, JavaScript, Java, Bash, Lua, Go, Rust, Elixir
  \item[Frameworks \& Libraries:] Ruby on Rails, Flask, React, Next.js, Node.js, Spring Boot, Phoenix
  \item[DevOps \& Infrastructure:] GitHub Actions, CircleCI, Linux, Docker, Aptible, Azure, AWS
  \item[Testing:] RSpec, JUnit, Jest, Enzyme, PyTest, Cypress, Pact
  \item[Data \& APIs:] GraphQL, REST APIs, ActiveRecord, SQLAlchemy, PostgreSQL, MySQL
  \item[Domain Expertise:] System Design, API Design, Data Modeling, CI/CD, DevEx, A11y, Globalization, Mentoring
  \item[Languages:] English, Hindi, Bengali, Spanish
\end{description}

\end{document}
